reOpt Data

### 2023-01-18 src/reopt.Rmd
selecting metric for each criteria

```{r}
Annual Renewable Electricity (%)
Lifecycle Total tons CO2
Internal Rate of Return (IRR) (%)
Lifecycle Costs of Health Emissions ($)

>>>>

```{r}
energy_production_metric <- reopt_data %>% 
  select(cbsa, city_msa, county, annual_renewable_electricity_percent_of_total) %>% 
  rename(annual_renewable_percent = annual_renewable_electricity_percent_of_total) %>% 
  mutate(annual_renewable_percent = annual_renewable_percent*100) %>% 
  # normalize data 
  mutate(normalized_annual_renewable = (annual_renewable_percent - min(annual_renewable_percent))/(max(annual_renewable_percent)-min(annual_renewable_percent)))

climate_impacts_metric <- reopt_data %>% 
  select(cbsa, city_msa, county, lifecycle_total_t_co2) %>%

financial_metric <- reopt_data %>% 
   select(cbsa, city_msa, county, irr)

health_emissions_costs <- reopt_data  %>% 
   select(cbsa, city_msa, county, lifecycle_costs_of_health_emissions_difference_from_bau
